Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-16 Ben_Manuscripts/structure_paper/supporting_information.tex
Some more changes.

  We chose to build all systems using 20 monomers per column. We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a small number of layers will cause the system to suffer from 
  finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (See
  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
  built with 40 monomers per column continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. Regardless, the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

@@

  \vspace{1em}
  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (See Figure~\ref{fig:stacking}). Our model is most consistent with experiment
  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
  the parallel displaced configuration.

@@

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 KJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
%		spacings is 3.96 nm.

@@

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
		larger than the experimental value. Once the restraining potential reaches 56
		KJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
		a linear trend (Figure~\ref{fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

		\caption{The pore spacing during the restrained portion of the
			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
			experimental value (a) or at the experimental value (b), there is an abrupt
			change in pore spacing when the position restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
			do not intersect with adjacent pores, and position restraints are reduced to 56
			KJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
			when force constants are reduced below 3 KJ mol$^{-1}$ nm$^{-2}$.} 
		\label{fig:p2p}
	  \end{figure}

@@

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~and the initial distance between layers
	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
	  as the average distance of all carbonyl carbons (See
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the time series
	  representing the average pore radius at each frame. We detected equilibration
	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
	  and standard deviation of pore radii using only data points collected after
	  equilibration was detected.

@@

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  % BJC: to be updated once simulations are run out long enough
	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
	  8 \AA   & $0.69 \pm 0.01$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{The average pore radii of systems built with an initial pore
		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
		  the pore radius is too large, slit pores may form.}~\label{table:radii}
	  \end{table}

@@

  We developed equilibration schemes to create dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. To create a dry configuration, we fix monomer head groups in the
  sandwiched or parallel-displaced configuration using position restraints with a
  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
  the NVT ensemble which allows the monomer tails to settle without disrupting
  the ordering of the head groups. Doing so also mitigates system dependence on
  initial monomer configuration. Every 50 ps, we reduce the force constants by
  the square root of its previous value. Once the force constant is below 10 KJ
  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
  with pressure controlled by the Berendsen barostat. Next, we run long NPT
  equilibration simulations for at least 400 ns using the Parrinello-Rahman
  barostat with a time constant of 10 ps.

@@

  \end{subfigure}
  \caption{The distribution of angles between nematic director vector (See
	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
	  of each trajectory}~\label{fig:nematic_distribution}
  \end{figure}

@@

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a Lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit parameters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on Lorentzian parameters
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{(a) We estimated the system's experimental correlation length using a 
  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a Lorentzian curve 
  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
  The correlation length is 1/FWHM.}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disordered Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  System & Diffusion Constant ($m^2/s$) \\ 
  \midrule
  Sandwiched, Ordered & $1.4\mathrm{e}{-14}$ \\
  Parallel Displaced, Ordered & $2.0\mathrm{e}{-14}$ \\
  Sandwiched, Disordered & $2.0\mathrm{e}{-14}$ \\
  Parallel Displaced, Disordered & $3.5\mathrm{e}{-14}$ \\
  \bottomrule
  \end{tabular}
  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
  which is three orders of magnitude lower than literature values.}~\label{table:msd}
  \end{table}

@@

  Persistent oscillations in the z-correlation function, $g(z)$, increase the intensity of R-$\pi$. 
  In Figure~\ref{fig:z_correlation}, we fit a decaying sinusoidal function 
  (equation~\ref{M-eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
  sandwiched configuration in the ordered basin. While the sinusoidal decay fit decays to one
  rather quickly, $g(z)$ continues to oscillate with nearly the same amplitude as its third peak. 
  In Figure~\ref{fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
  fit with a function that continues to oscillate with the same amplitude as the third peak of
  the fit to $g(z)$. In Figure~\ref{fig:power_spectrum_comparison}, we plot the power spectrum
  generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
  The maximum intensity of the power spectrum increases by nearly 60 \% when the correlation 
  function does not decay to one. This explains, in part, the large simulated value of the
  intensity of R-$\pi$.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{z_correlation_layered_sinefit.png}
  \caption{}\label{fig:z_correlation}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{theoretical_correlation_functions.png}
  \caption{}\label{fig:theoretical_correlation_functions}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{power_spectrum_comparison.png}
  \caption{}\label{fig:power_spectrum_comparison}
  \end{subfigure}
  \caption{(a) We fit a decaying sinusoidal function to the z-correlation function, $g(z)$, 
  calculated from the ordered basin sandwiched system. The oscillations in $g(z)$ continue
  to oscillate at nearly the same amplitude as its third peak. (b) We overlaid a plot of the
  fit to $g(z)$ with a similar function that continues to oscillate with the same amplitude
  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60 \% increase in
  intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
  \end{figure}

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.915\textwidth}
  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
  	\rowname{Parallel Displaced}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
  	\rowname{Sandwiched}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
  	\end{tabular}
  \end{subfigure}
  \begin{subfigure}{0.075\textwidth}
  	\includegraphics[width=\textwidth]{colorbar_jet.png}
  \end{subfigure}
	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
  \label{fig:solvation}

@@

  In the main text, we calculated ionic conductivity using the Nernst Einstein 
  relationship. We also measured ionic conductivity using a second method, 
  termed the Collective Diffusion model, for robustness. The collective 
  diffusion model measures the movement of the collective variable, Q, which
  is defined as the amount of charge transfer through the system and can be 
  thought to represent the center of charge of the system. The conductance, 
  $\gamma$, of the system can be calculated as:
  \begin{equation}
	 \gamma = \dfrac{D_Q}{k_b T} 
	\label{eqn:collective_diffusion}
  \end{equation}
  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
  calculated using the Einstein relation. We convert the resulting value
  to ionic conductivity by multiplying by channel length and dividing by
  the membrane cross sectional area. One can access a detailed derivation of 
  the model elsewhere\cite{liu_collective_2013}.

  \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
        \caption{The Collective Diffusion model and the Nernst-Einstein relation yield
        agreeing values of ionic conductivity for both types of ordered basin systems 
        simulated. Both methods estimate the value of the ionic conductivity to be an 
        order of magnitude higher than the experimental value. There is more noise in
        the collective diffusion model because there is inherently less data that 
        can be used for its calculation. For that reason, we use only the Nernst 
        Einstein relationship in the main text.}
        \label{fig:conductivity}
  \end{figure}

>>>>

  We chose to build all systems using 20 monomers per column. We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a small number of layers will cause the system to suffer from 
  finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
  built with 40 monomers per column continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. Regardless, the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

@@

  \vspace{1em}
  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (see Figure~\ref{fig:stacking}). Our model is most consistent with experiment
  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
  the parallel displaced configuration.

@@

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 kJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
%		spacings is 3.96 nm.

@@

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
		larger than the experimental value. Once the restraining potential reaches 56
		kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
		a linear trend (Figure~\ref{fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
		the restraining potential reaches 56 kJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 kJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

		\caption{The pore spacing during the restrained portion of the
			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 kJ
			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
			experimental value (a) or at the experimental value (b), there is an abrupt
			change in pore spacing when the position restraints are reduced to 56 kJ
			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
			spacing decreases nearly linearly once the restraints are reduced to 56 kJ
			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
			do not intersect with adjacent pores, and position restraints are reduced to 56
			kJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
			when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$.} 
		\label{fig:p2p}
	  \end{figure}

@@

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~and the initial distance between layers
	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
	  as the average distance of all carbonyl carbons (see
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the time series
	  representing the average pore radius at each frame. We detected equilibration
	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
	  and standard deviation of pore radii using only data points collected after
	  equilibration was detected.

@@

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
          %MRS8: nm to aa conversion error?
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  % BJC: to be updated once simulations are run out long enough
	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
	  8 \AA   & $0.69 \pm 0.01$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{The average pore radii of systems built with an initial pore
		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
		  the pore radius is too large, slit pores may form.}~\label{table:radii}
	  \end{table}

@@

  We developed equilibration schemes to create dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. To create a dry configuration, we fix monomer head groups in the
  sandwiched or parallel-displaced configuration using position restraints with a
  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
  the NVT ensemble which allows the monomer tails to settle without disrupting
  the ordering of the head groups. Doing so also mitigates system dependence on
  initial monomer configuration. Every 50 ps, we reduce the force constants by
  the square root of its previous value. Once the force constant is below 10 kJ
  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
  8, 3, 2, 1, and 0 kJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
  with pressure controlled by the Berendsen barostat. Next, we run long NPT
  equilibration simulations for at least 400 ns using the Parrinello-Rahman
  barostat with a time constant of 10 ps.

@@

  \end{subfigure}
  \caption{The distribution of angles between nematic director vector (see
	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
	  of each trajectory}~\label{fig:nematic_distribution}
  \end{figure}

@@

  \vspace{1em}
  Previous experimental studies of these systems did not calculate the correlation length, so we estimated it
  from the raw 2D WAXS data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a Lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit parameters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on Lorentzian parameters
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{(a) We estimated the system's experimental correlation length using a 
  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a Lorentzian curve 
  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
  The correlation length is 1/FWHM.}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disordered Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  %MRS8: at least one of these would be good to put in the main paper.
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  System & Diffusion Constant ($m^2/s$) \\ 
  \midrule
  Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
  Parallel Displaced, Ordered & $2.0 \times 10^{-14}$ \\
  Sandwiched, Disordered & $2.0 \times 10^{-14}$ \\
  Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
  \bottomrule
  \end{tabular}
  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
  which is three orders of magnitude lower than literature values.}~\label{table:msd}
  \end{table}

@@

  Persistent oscillations in the z-correlation function, $g(z)$, increase the intensity of R-$\pi$. 
  In Figure~\ref{fig:z_correlation}, we fit a decaying sinusoidal function 
  (equation~\ref{M-eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
  sandwiched configuration in the ordered basin. While the sinusoidal decay fit decays to one
  rather quickly, $g(z)$ continues to oscillate with nearly the same amplitude as its third peak. 
  In Figure~\ref{fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
  fit with a function that continues to oscillate with the same amplitude as the third peak of
  the fit to $g(z)$. In Figure~\ref{fig:power_spectrum_comparison}, we plot the power spectrum
  generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
  The maximum intensity of the power spectrum increases by nearly 60\% when the correlation 
  function does not decay to one. This explains, in part, the large simulated value of the
  intensity of R-$\pi$.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{z_correlation_layered_sinefit.png}
  \caption{}\label{fig:z_correlation}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{theoretical_correlation_functions.png}
  \caption{}\label{fig:theoretical_correlation_functions}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{power_spectrum_comparison.png}
  \caption{}\label{fig:power_spectrum_comparison}
  \end{subfigure}
  \caption{(a) We fit a decaying sinusoidal function to the z-correlation function, $g(z)$, 
  calculated from the ordered basin sandwiched system. The oscillations in $g(z)$ continue
  to oscillate at nearly the same amplitude as its third peak. (b) We overlaid a plot of the
  fit to $g(z)$ with a similar function that continues to oscillate with the same amplitude
  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60\% increase in
  intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
  \end{figure}

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.915\textwidth}
  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
  	\rowname{Parallel Displaced}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
  	\rowname{Sandwiched}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
  	\end{tabular}
  \end{subfigure}
  \begin{subfigure}{0.075\textwidth}
  	\includegraphics[width=\textwidth]{colorbar_jet.png}
  \end{subfigure}
	\caption{Adding 1 wt\% water to the ordered basin dry systems causes an increase in the intensity
	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
  \label{fig:solvation}

@@

  In the main text, we calculated ionic conductivity using the Nernst-Einstein 
  relationship. We also measured ionic conductivity using a second method, 
  termed the Collective Diffusion model, for robustness. The collective 
  diffusion model measures the movement of the collective variable, Q, which
  is defined as the amount of charge transfer through the system and can be 
  thought to represent the center of charge of the system. The conductance, 
  $\gamma$, of the system can be calculated as:
  \begin{equation}
	 \gamma = \dfrac{D_Q}{k_b T} 
	\label{eqn:collective_diffusion}
  \end{equation}
  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
  calculated using the Einstein relation. We convert the resulting value
  to ionic conductivity by multiplying by channel length and dividing by
  the membrane cross sectional area. One can access a detailed derivation of 
  the model elsewhere\cite{liu_collective_2013}.

  \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
        \caption{The Collective Diffusion model and the Nernst-Einstein relation yield
        agreeing values of ionic conductivity for both types of ordered basin systems 
        simulated. Both methods estimate the value of the ionic conductivity to be an 
        order of magnitude higher than the experimental value. There is more noise in
        the collective diffusion model because there is inherently less data that 
        can be used for its calculation. For that reason, we use only the Nernst-Einstein relationship in the main text.}
        \label{fig:conductivity}
  \end{figure}
